\documentclass{article}
\input{mypreamble/a-preamble}

%%%%% TITLE PAGE
\title{Shifted Symplectic Integration}

\begin{document}

\maketitle

\section{First Definitions}

We work with $\infty$-stacks on the $\infty$-category of connective commutative derived rings in characteristic $0$: equivalently defined as the sind-cocompletion of polynomial algebra (free finitely generated $k$-algebras), simplicial commutative algebra, CDGA in positive (homological) degree, connective $\mathcal{E}^\infty$-algebras in $k\amod$,... The topology is étale and the stacks must have a suitable theory of (co)tangent modules (it has to be a dualizable object), for example we can use Artin stacks.

Ideally, I'd like to study stacks on $\dMan$ at some point: the point is that geometric quantization should be more likely to exist in the $\mathcal{C}^\infty$-setting rather than the algebraic one. It probably won't change any of what follows.

\begin{remark}[Working on Points]
    Recall for a stack $X \in \aff^{\op} \to \Spa$, we define
\[
    \qcoh(X) = \Lim_{X} (\aff^{\op} \xto[-\amod] \Cat)
\]
by point-wise right Kan extension. Automatically, this implies that $qcoh$ sends colimits of (pre)stacks to limits (of categories).

Let us consider $F\in\B \to \st$ a finite diagram of stacks. Then $\Lim F$ is a stack and we have a correspondence between $A$-points $x$ of $\Lim F$ and cones on $A$ of $F$. We can define functors
\[
    \mathbb{L}_x \in \begin{cases}[rCl]
        \mathcal{B} &\longrightarrow& A\amod\\
        b &\longmapsto& x_b^*(\mathbb{L}_{Fb})
    \end{cases}
\]
and its linear dual $\mathbb{T}_x$. We then have
\[
    x^*\mathbb{L}_{\Lim F} = \Colim_{\mathcal{B}} \mathbb{L}_x \\
    x^*\mathbb{T}_{\Lim F} = \Lim_{\mathcal{B}} \mathbb{T}_x
\]
Using this, building (shifted) maps between tangent and cotangent modules is equivalent to building such maps the respective (co)limits on the $A$-points, naturally in the points.
\end{remark}

\begin{remark}[How about \textbf{closed} forms?] It's not clear to me yet, how one could translate being a closed form at points like this? It's probably not possible: I will have to deal with this eventually.
\end{remark}

Recall we have
% https://q.uiver.app/#q=WzAsMixbMCwwLCJcXE1vZCJdLFswLDIsIlxcRUFsZ3tcXGluZnR5fShrXFxNb2QpIl0sWzAsMSwiUlxcb3BsdXMgTSIsMV0sWzAsMSwiUiIsMCx7ImN1cnZlIjotMn1dLFsxLDAsIlxcbWF0aGJie0x9IiwwLHsiY3VydmUiOi0zfV0sWzQsMiwiXFxkYXNodiIsMSx7InNob3J0ZW4iOnsic291cmNlIjoyMCwidGFyZ2V0IjoyMH0sInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6Im5vbmUifSwiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dXQ==
\[\begin{tikzcd}
	\amod \\
	\\
	{\EAlg{\infty}(k\amod)}
	\arrow[""{name=0, anchor=center, inner sep=0}, "{R\oplus M}"{description}, from=1-1, to=3-1]
	\arrow["R", curve={height=-12pt}, from=1-1, to=3-1]
	\arrow[""{name=1, anchor=center, inner sep=0}, "{\mathbb{L}}", curve={height=-18pt}, from=3-1, to=1-1]
	\arrow["\dashv"{description}, draw=none, from=1, to=0]
\end{tikzcd}\]
where $R$ is a bifibration, $R\oplus M$ is a right adjoint and $\mathbb{L}$ its left adjoint. Furthermore, we have $R \circ \mathbb{L} \simeq 1$, meaning that the cotangent of $A$ is an $A$-module.

\section{Some Ideas}

What does the de Rham complex look like on a point?
Basically $d$ becomes $0$ but we still have symmetric powers of the cotangent at a point.
If we want to capture the behavior of $d$ we need to look at open covers, or something else.
The coefficient field is initial in CDGA and hence terminal in Aff. As a stack, it is also terminal. This gives a forgetful $\qcoh(X) \to k\amod$ and we can find $d$ in the image.

\section{Poincar\'e Duality}

Let $\B \to \Bsc$ be a tangential structure, \textit{i.e.} a right fibration. We have the following categories:
\[
    \Bsc(\mathcal{B})_+, \Bsc(\mathcal{B})^+ \longmono \ZBsc(\mathcal{B})
\]
where an object of $\Bsc(\mathcal{B})_+$ is a $\B$-basic adjointed a separate point $U\sqcup \{\infty\}$ and an object of $\Bsc(\mathcal{B})^+$ is a $\B$-basic adjointed a compactifying point $V^+$.
More explicitly, $\B \to \Bsc(\mathcal{B})_+$ canonically makes the hom-spaces pointed (by adding a discrete point), and $\Bsc(\mathcal{B})^+ \simeq \left(\Bsc(\mathcal{B})_+\right)^\op$ canonically.
In $\ZBsc(\mathcal{B})$, the hom-spaces between mixed types are either trivial or
\[
    \ZBsc(\mathcal{B})(U\sqcup \{\infty\}, V^+)
\]
which can be described by some simplicial set.

A functor $\B \to A\amod$ can be extended to $\Bsc(\mathcal{B})_+$ by using zero-maps and to $\Bsc(\mathcal{B})^+$ if it lands into dualizable objects.

Our goal is to prove the following: 
\begin{theorem}
    A functor $\mathcal{B}$ to stacks extends to a functor... if and only if it factors though.. 
\end{theorem}

\subsection{Examples}

\begin{enumerate}
    \item $\{\bullet\} \to \Bsc^{fr}$ picking $\mathbb{R}^n$ gives an object $A$ together with an isomorphism $A \simeq A^\vee[n]$
\end{enumerate}

\section{Geometric Quantization}

\begin{definition}
    A \textbf{polarization} is a Lagrangian foliation. More explicitly, 
\end{definition}

\end{document}
